### 2018-07-30 Paper/intro.tex
..

The emerging field of uncertainty quantification (UQ) aims at methodologies for
incorporating, characterizing, quantifying, propagating, and reducing the
uncertainties associated with predictive models and simulations.  For
situations involving complex physical models and computationally intensive
simulations, surrogate modeling often provides orders of magnitude speedups in
statistical studies. This is done by replacing repeated evaluations of
computationally expensive models by inexpensive evaluations of a surrogate
model.  Thus, an efficient approach to construction of surrogate models is of
central importance in enabling efficient uncertainty quantification for
computationally intensive models.

Commonly used surrogate modeling approaches use polynomial chaos expansions
(PCEs)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}, multivariate adaptive
regression splines (MARS)~\cite{friedman93}, Gaussian processes
(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}.  Many real-world
applications involve a large number of model inputs. This makes
the construction of surrogate models difficult or impossible in some cases.
However, in many situations, the variability in model observables of interest
is sensitive to only a small subset of the uncertain inputs.  Hence,
identifying model inputs that are inessential to variability in model output is
a key step that can help reduce the input parameter dimension and hence the effort
associated with surrogate model construction.

@@

Variance based global sensitivity analysis based on Sobol' indices~\cite{Sobol93,
Sobol:2001,
Owen13,
SaltelliRattoAndresEtAl08} provides
insight into the relative contributions of the uncertain model inputs to the
uncertainty in predictions. Specifically, such analysis can help reduce the
dimensionality of the problem.  Computing Sobol' indices, however, is a
computationally demanding task.  
Availability of a surrogate model typically
enables efficient computation 
of Sobol' indices~\cite{Sudret08,CrestauxLeMaitreMartinez09,BlatmanSudret10,HartAlexanderianGremaud17,Sargsyan17}. This has enabled performing global sensitivity analysis
on a wide range of applications including in ocean 
modeling~\cite{AlexanderianWinokurSrajEtAl12,LiIskandaraniLeHenaffEtAl16},
geosciences~\cite{Namhata2016OladyshkinDilmoreEtAl16,deman2016,SaadAlexanderianPrudhommeEtAl17},
and chemical kinetics~\cite{DegasperiGilmore08,navarro2016global,Vohra:2014}
to name a few.

While surrogate models provide an efficient way of computing sensitivity
indices, constructing them in the case of models with high-dimensional inputs
can be as expensive as computing the Sobol' indices via sampling. 
In this article, we propose a practical and efficient
approach to address this commonly observed ``chicken-and-egg'' problem
in surrogate modelling for engineering applications.
Specifically, we reduce
the dimensionality of the input space using derivative-based global sensitivity
analysis~\cite{Sobol:2009,Sobol:2010,Lamboni:2013,Kucherenko:2009,Kucherenko:2016},
which enables a tractable approach for global sensitivity
analysis~\cite{Kucherenko:2016}. The links between derivative based
global sensitivity measures (DGSMs) and total Sobol'
indices~\cite{Sobol:2009,Kucherenko:2009,Kucherenko:2016} provide a strong
basis for their use in identifying unimportant parameters. In addition
to the construction of an efficient surrogate in the reduced space,
dimension reduction highlights key features of the input-output relationship
encapsulated by the model, and allows for an efficient approach to calibration
of the important inputs.

>>>>

\paragraph{Motivation}
Surrogate modeling has become a critical component of scientific computing
owing to the emergence of the field of uncertainty quantification for
scientific and engineering applications. Commonly used approaches for
surrogate modeling include polynomial chaos expansions
(PCEs)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}, multivariate adaptive
regression splines (MARS)~\cite{friedman93}, Gaussian processes
(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}. A 
pertinent challenge associated with surrogate construction involves the
process of \textit{training} that typically requires a large number of model runs.
In situations involving large-dimensional systems,
and computationally intensive simulations, the training of a surrogate
becomes remarkably challenging and even prohibitive in some cases. A possible
approach for mitigating this challenge involves computation of sensitivity
measures (e.g. Sobol' indices~\cite{Sobol93,Sobol:2001,Owen13,SaltelliRattoAndresEtAl08})
to ascertain important parameters that predominantly contribute towards the variability
of the model output. Sensitivity-based dimension reduction could thus help
reduce the computational effort significantly. However, numerically estimating
the Sobol' indices that involve multi-dimensional integrals can be a demanding task
in itself. In fact, surrogate models are constructed to estimate the 
Sobol sensitivity indices for a variety of applications including in ocean 
modeling~\cite{AlexanderianWinokurSrajEtAl12,LiIskandaraniLeHenaffEtAl16},
geosciences~\cite{Namhata2016OladyshkinDilmoreEtAl16,deman2016,SaadAlexanderianPrudhommeEtAl17},
and chemical kinetics~\cite{DegasperiGilmore08,navarro2016global,Vohra:2014}
to name a few. Hence, this common practical issue in scientific computing can
be characterized as a ``chicken-and-egg" problem.

In this article, we propose a practical and efficient approach that focuses on
optimal use of computational resources for surrogate construction in a 
reduced-input space. Specifically, we reduce the dimensionality of the
input space by using the derivative-based global sensitivity
analysis~\cite{Sobol:2009,Sobol:2010,Lamboni:2013,Kucherenko:2009,Kucherenko:2016},
which enables a tractable approach for global sensitivity
analysis~\cite{Kucherenko:2016}. The links between derivative based
global sensitivity measures (DGSMs) and total Sobol'
indices~\cite{Sobol:2009,Kucherenko:2009,Kucherenko:2016} provide a strong
basis for their use in identifying unimportant parameters. In addition
to the construction of an efficient surrogate in the reduced space,
dimension reduction highlights key features of the input-output relationship
encapsulated by the model, and allows for an efficient approach to calibration
of the important inputs.

%The emerging field of uncertainty quantification (UQ) aims at methodologies for
%incorporating, characterizing, quantifying, propagating, and reducing the
%uncertainties associated with predictive models and simulations.  For
%situations involving complex physical models and computationally intensive
%simulations, surrogate modeling often provides orders of magnitude speedups in
%statistical studies. This is done by replacing repeated evaluations of
%computationally expensive models by inexpensive evaluations of a surrogate
%model.  Thus, an efficient approach to construction of surrogate models is of
%central importance in enabling efficient uncertainty quantification for
%computationally intensive models. 
%
%
%Commonly used surrogate modeling approaches use polynomial chaos expansions
%(PCEs)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}, multivariate adaptive
%regression splines (MARS)~\cite{friedman93}, Gaussian processes
%(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}.  Many real-world
%applications involve a large number of model inputs. This makes
%the construction of surrogate models difficult or impossible in some cases.
%However, in many situations, the variability in model observables of interest
%is sensitive to only a small subset of the uncertain inputs.  Hence,
%identifying model inputs that are inessential to variability in model output is
%a key step that can help reduce the input parameter dimension and hence the effort
%associated with surrogate model construction.

@@

%Variance based global sensitivity analysis based on Sobol' indices~\cite{Sobol93,
%Sobol:2001,Owen13,SaltelliRattoAndresEtAl08} provides
%insight into the relative contributions of the uncertain model inputs to the
%uncertainty in predictions. Specifically, such analysis can help reduce the
%dimensionality of the problem.  Computing Sobol' indices, however, is a
%computationally demanding task.  
%Availability of a surrogate model typically
%enables efficient computation 
%of Sobol' indices~\cite{Sudret08,CrestauxLeMaitreMartinez09,BlatmanSudret10,HartAlexanderianGremaud17,Sargsyan17}. This has enabled performing global sensitivity analysis
%on a wide range of applications including in ocean 
%modeling~\cite{AlexanderianWinokurSrajEtAl12,LiIskandaraniLeHenaffEtAl16},
%geosciences~\cite{Namhata2016OladyshkinDilmoreEtAl16,deman2016,SaadAlexanderianPrudhommeEtAl17},
%and chemical kinetics~\cite{DegasperiGilmore08,navarro2016global,Vohra:2014}
%to name a few.
%
%While surrogate models provide an efficient way of computing sensitivity
%indices, constructing them in the case of models with high-dimensional inputs
%can be as expensive as computing the Sobol' indices via sampling. 
%In this article, we propose a practical and efficient
%approach to address this commonly observed ``chicken-and-egg'' problem
%in surrogate modelling for engineering applications.
%Specifically, we reduce
%the dimensionality of the input space using derivative-based global sensitivity
%analysis~\cite{Sobol:2009,Sobol:2010,Lamboni:2013,Kucherenko:2009,Kucherenko:2016},
%which enables a tractable approach for global sensitivity
%analysis~\cite{Kucherenko:2016}. The links between derivative based
%global sensitivity measures (DGSMs) and total Sobol'
%indices~\cite{Sobol:2009,Kucherenko:2009,Kucherenko:2016} provide a strong
%basis for their use in identifying unimportant parameters. In addition
%to the construction of an efficient surrogate in the reduced space,
%dimension reduction highlights key features of the input-output relationship
%encapsulated by the model, and allows for an efficient approach to calibration
%of the important inputs.
